\LARGE How coexistence mechanisms mediate temporal stability

### 2016-02-22 manuscript/manuscript.Rmd
new intro intro

## rmarkdown render options
output:
  pdf_document:
    fig_caption: true
    keep_tex: true
fontsize: 12pt
geometry: margin=1in

@@

Introduction
------------
It is now clear that species richness tends to increase the temporal stability of biomass production in competitive plant communities. It is even becoming clear that a few core mechanisms related to compensatory dynamics among species through temporal or functional complementarity can explain the positive relationship between diversity and stability. What remains unclear is how the coexistence mechanism that maintains species richness influences the strength of compensatory dynamics. Theoretical studies based on Lotka-Volterra models have given us insight into the mechanisms that promote stability in communities where species coexist by fluctuation-independent mechanisms. A remaining challenge is to explore the importance of proposed mechanisms behind diversity-stability relationships in communities where species coexistence is maintained by temporal variability. Specifically, we seek to understand the mechanisms that promote temporal stability in communities where species coexistence is achieved because of temporal variability.

>>>>

## rmarkdown render options
output:
  pdf_document:
    fig_caption: true
    keep_tex: false
fontsize: 12pt
geometry: margin=1in

@@

Introduction
------------
Species-specific responses to non-constant environmental conditions can stabilize species coexistence [@Chesson2000] and ecosystem function [@Loreau2010].
This means that fluctuation-dependent mechanisms of species coexistence are the very same mechanisms that link biodiversity and ecosystem function.
Yet, the theory that has developed over the past 20 years to explain the, generally, positive relationship between species richness and stability of ecosystem function has implicitly assumed species coexistence [@Loreau2010], or, when explicitly considered, coexistence is maintained by fluctuation-independent mechanisms [@Turnbull2012].
Despite rapid theoretical developments in the fields of species coexistence and biodiversity-ecosystem function, a gulf remains between the two lines of inquiry [@Turnbull2012].
This is especially surprising since stable coexistece, however maintained, is a preqrequisite for biodiversity to confer stability of ecosystem function in the long term.
